---
title: "Sentiment_Likes"
author: "Josh Kong"
date: "5/14/2020"
output: pdf_document
---

```{r}
library(dplyr)
library(tidytext)
library(textdata)
library(tidyr)
library(ggplot2)
library(tidyverse)
```


```{r}
posts <- read_csv("Datasets/politicians_ig.csv")
followers <- read_csv("Datasets/poli_ig_followers.csv")
```


```{r}
#used this to make sure names in followers matched with sentiment
for (i in 1:nrow(followers))
{
  if(followers$name[i] == "barackobama")
  {
    followers$name[i] <- "Barack Obama"
  }
  else if(followers$name[i] == "berniesanders")
  {
    followers$name[i] <- "Bernie Sanders"
  }
  else if(followers$name[i] == "elizabethwarren")
  {
    followers$name[i] <- "Elizabeth Warren"
  }
  else if(followers$name[i] == "realdonaldtrump")
  {
    followers$name[i] <- "President Donald J. Trump"
  }
  else if(followers$name[i] == "sentedcruz")
  {
    followers$name[i] <- "Ted Cruz"
  }
  else if(followers$name[i] == "joebiden")
  {
    followers$name[i] <- "Joe Biden"
  }
}
#used this to make sure the dates matched 
followers <- followers %>% rename(mdy_time = date)
followers$mdy_time <- str_replace_all(followers$mdy_time,"April","Apr")
followers$mdy_time <- str_replace_all(followers$mdy_time,"March","Mar")
followers$mdy_time <- str_replace_all(followers$mdy_time,"February","Feb")
followers$mdy_time <- str_replace_all(followers$mdy_time,"January","Jan")
followers$mdy_time <- str_replace_all(followers$mdy_time,"December","Dec")
followers$mdy_time <- str_replace_all(followers$mdy_time,"November","Nov")
```


```{r}
captions <- posts %>% select(caption,post_url,mdy_time,views,likes, name) %>% as_tibble()
captions <- captions %>% unnest_tokens(word, caption)# unnest captions into individual words
stop_words_es <- stopwords::stopwords("es", source = "stopwords-iso")
stop_words_fr <- stopwords::stopwords("fr", source = "stopwords-iso")
stop_words_en <- stopwords::stopwords("en", source = "stopwords-iso")
stop_words_latin <- c(stop_words_es,stop_words_fr,stop_words_en)
stop_words_latin <- data.frame("word" = stop_words_latin, lexicon = 'SMART',stringsAsFactors = F)
captions <- captions %>% anti_join(stop_words_latin) # remove articles like the, and, a..,

```
Separated the individuals words in the caption.

```{r}
#how much likes each post has
likes <-  posts %>% select(name,likes,post_url) %>% na.omit()
#sentiment_per_post is how much sentiment each post has
sentiment_per_post <- captions %>% select(word, mdy_time, name, post_url) %>% inner_join(get_sentiments("afinn"))
sentiment_per_post <- sentiment_per_post %>%  group_by(post_url,name,mdy_time) %>%  summarise(sentiment =sum(value)) %>% arrange(name)

#sentiment_likes just shows sentiment per post with the number of likes per post
sentiment_likes <- sentiment_per_post %>%select(name,post_url,sentiment,mdy_time) %>%  inner_join(likes)

```
Using the get_sentiments() function, I measured the amount of sentiment each of the politician's posts had.

I then combined it with another data to see how much likes and sentiment each post had.


```{r}
ggplot(sentiment_likes, aes(x = sentiment, y = likes)) + geom_point() + labs(title = "Sentiment's Effect on Likes") 
```
This is the plot to see the relationship between the sentiment score in a post and the number of likes.

This data may be skewed due to the difference in followers between the politicians. For example, Barack Obama has 27 million followers in Instagram compared to Joe Biden's 2 million followers.

To address the difference in followers, I decided to measure the proportion of followers that liked the post rather than total likes. 

```{r}
#sentiment_followers shows sentiment per post with the proportion of followers that liked the post
sentiment_followers <- sentiment_likes %>% left_join(followers, by = c( "mdy_time","name"))
sentiment_followers <- sentiment_followers %>% mutate(Proportion = likes/followers)

ggplot(sentiment_followers, aes(x = sentiment, y = Proportion)) + geom_point() + labs(title = "Sentiment's Effect on Likes")
```
This is the plot that shows the effect that sentiment has on the proportion of likes on a post.






